A generalized quadratic estimate for random field nonstationarity \thanksref{code}

### 2016-03-11 paper/paper.tex
fixed up imsart bib style

\documentclass[10pt,noinfoline]{imsart}
\usepackage{palatino}

\usepackage{bm}
\usepackage{geometry}
\usepackage{graphics,epsfig,rotate,lscape,graphicx,amsmath,amsthm,amssymb,float,amsfonts,amsbsy,hyperref,delarray,sectsty,amsfonts,amscd,pifont}
\usepackage[mathscr]{euscript}  % gives a different type of mathcal
\usepackage{multirow}
\usepackage{soul,float}
\usepackage{mathrsfs}
\usepackage{epsf}
\usepackage{psfrag}
%\usepackage{verbatim}
\usepackage{fancyvrb}
\usepackage{enumerate}
\usepackage{subfigure}
\usepackage{algorithmicx}
\usepackage{algorithm}

%----- for side captions
 \usepackage{sidecap}

%---- for shading regions
\usepackage{framed}
\usepackage[usenames,dvipsnames]{color}
\definecolor{shadecolor}{gray}{0.90}

% ---- for bib
\usepackage{natbib}

\geometry{letterpaper,left=1.2in,right=1.2in,top=1.2in,bottom=1.2in}
\bibliographystyle{plain}

\newtheorem{claim}{Claim}
\newtheorem{proposition}{Proposition}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{conjecture}{Conjecture}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\renewcommand{\labelenumi}{(\roman{enumi})}
\newcommand{\bs}{\boldsymbol}

>>>>

\documentclass[10pt,noinfoline]{imsart}

%\usepackage[OT1]{fontenc}
\usepackage{palatino}
\usepackage{bm}
\usepackage{geometry}
\usepackage{graphics,epsfig,rotate,lscape,graphicx,amsmath,amsthm,amssymb,amsfonts,amsbsy,delarray,sectsty,amscd,pifont}
\usepackage[mathscr]{euscript}  % gives a different type of mathcal
\usepackage{multirow}
\usepackage{soul,float}
\usepackage{mathrsfs}
\usepackage{epsf}
\usepackage{psfrag}
%\usepackage{verbatim}
\usepackage{fancyvrb}
\usepackage{enumerate}
\usepackage{subfigure}
\usepackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage[usenames,dvipsnames]{color}

%----- for algorithms
%\usepackage{algorithmicx}
%\usepackage{algorithm}

%----- for side captions
%\usepackage{sidecap}

%---- for shading regions
%\usepackage{framed}
%\usepackage[usenames,dvipsnames]{color}
%\definecolor{shadecolor}{gray}{0.90}

% ---- for bib
\usepackage[numbers]{natbib}
\bibliographystyle{plain}

\geometry{letterpaper,left=1.2in,right=1.2in,top=1.2in,bottom=1.2in}

%\startlocaldefs
\definecolor{shadecolor}{gray}{0.90}
\newtheorem{claim}{Claim}
\newtheorem{proposition}{Proposition}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{conjecture}{Conjecture}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\renewcommand{\labelenumi}{(\roman{enumi})}
\newcommand{\bs}{\boldsymbol}
%\endlocaldefs
